quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-04-08 paper-quollr.Rmd
Updated layout models

## Compute hexbin parameters
num_bins_x_limb <- 25

@@

distance_df_small_edges_limb <- distance_limb |>
  filter(distance < benchmark_limb) #benchmark_limb

@@

@@

distance_df_small_edges_limb <- distance_limb |>
  filter(distance < benchmark_limb) #benchmark_limb

>>>>

@@

tr_from_to_df_limb <- tr_from_to_df_limb |>
  mutate(ID = row_number()) |>
  filter(!(ID %in% c(108, 99, 11, 231)))

distance_df_small_edges_limb <- distance_limb |>
  filter(distance < 0.1) #benchmark_limb

@@

## Compute hexbin parameters
num_bins_x_limb <- 18

@@

tr_from_to_df_limb <- tr_from_to_df_limb |>
  mutate(ID = row_number()) |>
  filter(!(ID %in% c(298, 34, 48, 326)))

distance_df_small_edges_limb <- distance_limb |>
  filter(distance < benchmark_limb) #|>
  #mutate(ID = row_number()) |>
  #filter(!(ID %in% c(298, 34, 48))) |>
  #select(-ID) #benchmark_limb
